Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen.

Configuration errors were
reported to be the largest fraction of failures in storage systems in a 2014 industry
survey~\cite{yin11anempirical}.

Configuration errors are one of the most important root causes of today's 
software system failures~\cite{xu15systems, yin11anempirical}.
In their empirical study, Yin {\em et al.}~\cite{yin11anempirical} report 
that about 31\% of system failures were caused by misconfiguration problems
and only 20\% were caused by bugs in program code. 
Misconfigurations, in practice, may result in various system-wide problems,
including security vulnerabilities, application crashes, severe disruptions
in software functionality, 
and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}.  
Therefore, how to automatically verify configuration files is an open
problem~\cite{xu15systems}.

To the best of our knowledge, there have been several prior 
efforts that attempt to verify 
configuration files~\cite{santolucitoCAV, xu16early,
zhang14encore, huang15confvalley}.
However, state-of-the-art efforts either are impractical to be used
in reality, or can only deal with simplistic configuration errors.
In general, these efforts fall into two categories.

\squishlist

\item On the one hand are tools that can detect sophisticated 
configuration errors, \eg, ConfigC~\cite{santolucitoCAV}. 
However, these tools heavily rely on datasets containing 100\% 
correct configuration files to extract configuration rules.
Existing investigation studies~\cite{wang04automatic, yin11anempirical}
have demonstrated determining or obtaining 100\% correct configuration
files to drive rules is almost impossible in reality. 
Without 100\% correct datasets, these tools would, unfortunately, 
work poorly.

\item On the other hand, practical efforts, 
\eg, EnCore~\cite{zhang14encore} and
ConfValley~\cite{huang15confvalley}, can only 
detect simplistic configuration errors (\eg, value range errors 
and simple integer correlation errors), but cannot detect
sophisticated configuration errors. 
Consider entry ordering errors, 
which happen when some entries are inserted in a wrong order
in the configuration files. 
For example, in a PHP configuration file, 
an entry \code{extension=mysql.so} appears 
before \code{extension=recode.so},  
it would cause Apache server to crash. The correct ordering 
should be \code{extension=recode.so} before 
\code{extension=mysql.so}~\cite{yin11anempirical}.
Nevertheless, these types of errors cannot be detected by above existing
efforts.

\squishend

The goal of this work is to propose and build a {\em practical} 
configuration
verification tool capable of checking {\em sophisticated} 
configuration errors (more details
for sophisticated configuration errors in Sec.~\ref{sec:motiv}).
Achieving this goal requires us addressing two main obstacles:
1) the lack of a specification describing properties of configuration
files, and 2) the structure of configuration files---they are 
mainly a sequence of entries assigning some values to system
parameters (called keywords).
In other words, the ``language'' in which configuration 
files are written does not adhere to any specific grammar or syntax. 
Moreover, the entries in configuration files 
lack type or rules specifying constraints on entries, 
and there is no explicit structure policy for these entries.

>>>>

The systems research community has recognized this as an important
problem~\cite{xu16early}. While many efforts have been proposed to check, troubleshoot, diagnose, and repair configuration 
errors~\cite{attariyan10automating,
su07autobash, whitaker04configuration},
those tools mainly try to understand {\emph{what}} caused the 
error -- they are still not on a level of
automatic verification tools used for regular program 
verification~\cite{Leino10Dafny, PiskacWZ14, BobotFMP15} that can
detect errors without executing the code. In this paper we propose
a framework for automated verification of configuration files: we are analyzing 
files and proactively reporting potential errors, without waiting for them to happen. We developed a tool, called \app, and tested it on 
almost a thousand file from github.

We believe there are two main obstacles 
to why we cannot simply apply  the existing automatic 
tools and techniques to verification of configuration files:
1) the lack
of a specification describing properties of configuration files;
2) the structure of configuration files -- they
are mainly a sequence of entries assigning some value to system
variables (called {\emph {keywords}}). 
The language in which configuration files are written does 
not adhere to a specific grammar or syntax. In particular, the
entries in configuration files are untyped. Moreover, there are surprisingly few rules specifying constraints on entries, and there
is no explicit structure policy for the entries.

\app overcomes the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specification for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we learn specification from 
a large sample of 
configuration files~\cite{configdataset}. The first step is to 
translate this training set into a more structured typed representation.
We then apply the learning process and we learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties keywords in configuration files need to satisfy.
The learning process is language-agnostic and works for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or HTTPD configuration files).
We see this learning process as 
a way of deriving  a specification for configuration files. 
It is hard to talk here about a complete specification, but it is still
a set of formal rules describing the properties that configuration files need to satisfy.

Having a specification, \app can then efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.

There have been several prior efforts that attempt to verify 
configuration files~\cite{santolucitoCAV, xu16early,
zhang14encore, huang15confvalley}.
However, state-of-the-art efforts either are impractical to be used
in reality, or can only deal with simplistic configuration errors.
In general, these efforts fall into two categories.\begin{itemize}
\item On the one hand there are tools that can detect sophisticated 
configuration errors, \eg, ConfigC~\cite{santolucitoCAV}. 
However, these tools heavily rely on datasets containing 100\% 
correct configuration files to extract configuration rules.
Existing investigation studies~\cite{wang04automatic, yin11anempirical}
have demonstrated determining or obtaining 100\% correct configuration
files to drive rules is almost impossible in reality. 
Without 100\% correct datasets, these tools do not work.
\item On the other hand there are tools, 
\eg, EnCore~\cite{zhang14encore} and
ConfValley~\cite{huang15confvalley}, that can only 
detect rather simplistic configuration errors (\eg, value range errors 
and simple integer correlation errors), but cannot detect
more complex configuration errors, such as ordering errors or 
Nevertheless, these types of errors cannot be detected by above existing
efforts.
\end{itemize}
